Equipo 7

### 2021-05-03 final/script.Rmd
Update script.Rmd

#limpieza
planea_15 <- planea_15[-c(1:2),]
planea_19 <- planea_19[-c(1:7),]
```

@@

>>>>

#limpieza
planea_15 <- planea_15[-c(1:2),]
planea_19 <- planea_19[-c(1:7),]

#Ahora datos del 2010
censo_10<-read.csv("censo2010.csv")
planea_10<-read.csv("ENLACE_sec_2010.csv")

@@

#Para censo del 2010

names2<-c('vivtot','tvivpar','vivparhab', #localidad
         'vph_inter','vph_pc') #internet y laptop
for (i in names2){
  censo_10[[i]] <- as.numeric(censo_10[[i]])
}

#creo la base de datos de interes
censo_localidad10<-censo_10 %>% 
  select(Entidad,Municipio,Localidad,     #localidad           
         vivtot,tvivpar,vivpar_hab,       # vivienda
         vph_inter,vph_pc)   %>%    # internet y laptop
  mutate(internet=vph_inter*100/vivtot,
         lap=vph_pc*100/vivtot)

#cambio todo a mayus
censo_localidad10 <- as.data.frame(t(apply(censo_localidad10,1,toupper)))
